---
title: "tutoring-summer2022-intror"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# First, on .rmd files, code chunks, and commenting out in the code chunks


# 1 - making a code chunk
```{r}

```

# 2 - comment out something in a code chunk
```{r}

1 + 1 

## hey, this is a comment 
## so i can remember why i wrote this code... when i look back
## in 2 years...
```


# Let's get started - print "my name is ____"
```{r}

print("My name is Alyssa!")

print("123")

print(57)

1+2

an_interesting_quantity <- 1+2

an_interesting_quantity

```

# Find the sum of 1 2 and 3
```{r}

1 + 5 + 3

sum(1,5,3)

list_of_numbers <- c(1,2,3,4,5)

list_of_numbers

mean(list_of_numbers)

(1+2+3+4+5)/5

median(list_of_numbers)

our_function <- function(first_ingredient, second_ingredient){
  
  sum <- first_ingredient + second_ingredient
  
  interesting_quantity <- sum/(sum)^2
  
  print(interesting_quantity)

}


```

# Calculate 2 plus 2
# 100 divided by 23
# 7998 minus 1242
# 72 times 87

```{r}



```

# FUNCTIONS
# Two parts of a function - what are they?
# 1 - the name
# 2 - the inputs
# A function is like a recipe
# The things in parentheses are the ingredients
# Make a function that adds 1 plus 2 and outputs the answer
# call the function "mysum"
```{r}
mysum <- function(x,y){
  sum(x,y)
}
```

# Now make another function
# That takes 3 numbers, sums them, and multiplies that sum by the first number 
# squared
# ask it to print the result of this operation
# Call the function "mysecondfunction"
```{r}
mysecondfunction <- function(a,b,c){
  sum <- a + b + c
  result <- sum*(a^2)
  print(result)
}

mysecondfunction(1,2,3)

```

# Histograms

```{r}
# First make a "dataset"

inches_of_rain_in_monsoon <- c(1,3,4,2,1,2,5,5,5,5,5,6,6,6,2,2,1,4,5,6,2,3,4,1)
cm_of_rain_in_monsoon <- c(1,3,4,2,1,2,5,5,5,5,5,6,6,6,2,2,1,4,5,6,2,3,4,1)

data_variable_2 <- c(1,2,3)

hist(data_variable_2)

our_data_set <- as.data.frame(cbind(inches_of_rain_in_monsoon, cm_of_rain_in_monsoon))

hist(our_data_set$inches_of_rain_in_monsoon)

# Based on this vector, which number occurs the most frequently?

inches_of_rain_in_monsoon

# What is the mean?

mean(inches_of_rain_in_monsoon)

median(inches_of_rain_in_monsoon)

# Let's make a histogram

hist(inches_of_rain_in_monsoon)

# Let's make it blue

hist(inches_of_rain_in_monsoon, col = c("blue"))

# Let's change the main title

hist(inches_of_rain_in_monsoon, main="Rainfall in June", col = c("red"))

# Let's change the x axis

hist(inches_of_rain_in_monsoon, main="Rainfall in June", xlab = "Rainfall (in inches)",col = c("blue"))


```


